No Detectable Evidence of Genetic Associations with Anadromous and Resident Masu Salmon Sampled within Hokkaido

### 2022-06-01 paper/paper_draft.Rmd
hash

#Abstract

@@

##Genotyping

@@

```{r Figure_1_print,echo=FALSE,warning=FALSE,fig.cap="Figure 1: Association across the genome with migratory status showing that no loci were found that were significantly associated with the given traits (anadromy and residency)",fig.width=7, fig.height=4, fig.align='center', fig.cap.style="Image Caption"}
figure_1$plot

@@

```{r Figure_2_print,echo=FALSE,warning=FALSE,fig.cap="Figure 2: PCA plot showing the relatedness between anadromous and resident individuals in TK and CH populations",fig.width=7, fig.height=4, fig.align='center', fig.cap.style="Image Caption"}
p1

>>>>

# Abstract

Within Masu salmon (Oncorhynchus masou), individuals can exhibit one of two life histories: resident individuals which stay in streams for their entire life span or anadromous individuals which move to the ocean to mature before returning to their natal streams to breed. Current research has suggested that the expression of either life history is mainly influenced by environmental factors such as temperature, which influence critical traits like salmon's body size, growth rate, lipid stores. Here, we use high-resolution reduced-representation genome sequencing to show that there are no significant genetic associations with migratory decision making in masu salmon in two streams in Hokkaido, Japan. Further research with a larger sample size from more parts of the masu range is needed in order to fully assess potential genetic influences on anadromy and residency in the species.

# Introduction

@@

## Genotyping

@@

```{r Figure_1_print,echo=FALSE,warning=FALSE, include=TRUE,fig.cap="Figure 1: Association across the genome with migratory status showing that no loci were found that were significantly associated with the given traits (anadromy and residency)",fig.width=7, fig.height=4, fig.align='center', fig.cap.style="Image Caption"}
figure_1$plot

@@

```{r Figure_2_print,echo=FALSE,warning=FALSE,include=TRUE,fig.cap="Figure 2: PCA plot showing the relatedness between anadromous and resident individuals in TK and CH populations",fig.width=7, fig.height=4, fig.align='center', fig.cap.style="Image Caption"}
p1
